---
title: "NASIS data to EDIT"
author: "Nathan Roe"
date: "2/10/2022"
output: html_document
---

#### Packages
```{r, message=FALSE, warning=FALSE}
library(plyr)
library(dplyr)
library(httr)
library(wordcloud)
library(wordcloud2)
library(pander)
```

**Read in NASIS report**
```{r}
EDIT_updates <- read.csv("C:/Users/Nathan.Roe/Documents/PES4ever/NASIS_data_for_EDIT.csv")
```

**Remove miscellaneous areas**
```{r}
EDIT_updates <- EDIT_updates %>% filter(compkind != "miscellaneous area")
```


**Define ecosite of interest**
```{r}
EDIT_updates_filtered <- EDIT_updates %>% filter(ecosite_id == 'R018XD066CA')
```

#### **Physiographic features tab:**

**Landform**

Add the most relevant landforms. Try to keep it to 3-4. 
```{r}
landform <- as.data.frame(table(EDIT_updates_filtered$landform)) %>% 
  rename(Landform = Var1) %>% arrange(desc(Freq)) %>% mutate_if(is.factor, as.character)

landform
```

**Landform words**
```{r, warning=FALSE, message=FALSE}
landform_text <- paste(landform$Landform, collapse = " ")

words <- strsplit(landform_text, "[[:space:]]+")[[1]]

if(length(words) == 0){print("No landform descriptions")} else{wordcloud::wordcloud(words)
}
```

**Runoff class**
```{r}
# This field is obsolete and will be removed from EDIT. Enter medium for all values. 
```

**Flooding**

Put "--" for duration if frequency is "none"
```{r}
Flood.freq <- ifelse(EDIT_updates_filtered$flood_freq == "", "none", EDIT_updates_filtered$flood_freq)

as.data.frame(table(Flood.freq)) %>% 
  arrange(desc(Freq))

barplot(table(Flood.freq), main = "Flooding frequency")
```

```{r}
Flood.duration <- ifelse(EDIT_updates_filtered$flood_dur == "", "none", EDIT_updates_filtered$flood_dur)


as.data.frame(table(Flood.duration)) %>% arrange(desc(Freq))

barplot(table(Flood.duration), main = "Flooding duration")
```

**Ponding**

Put "--" for duration if frequency is "none"
```{r}
as.data.frame(table(EDIT_updates_filtered$pond_freq)) %>% 
  rename("Ponding Freq" = Var1) %>% arrange(desc(Freq))

barplot(table(EDIT_updates_filtered$pond_freq), main = "Ponding frequency")
```

```{r}
Pond.dur <- ifelse(EDIT_updates_filtered$pond_dur == "", "none", EDIT_updates_filtered$pond_dur)

as.data.frame(table(EDIT_updates_filtered$pond_dur)) %>% 
  rename("Ponding Duration" = Var1) %>% arrange(desc(Freq))

barplot(table(Pond.dur), main = "Ponding duration")
```

**Elevation range**
```{r, figures-side, fig.show="hold", out.width="50%"}
{hist(EDIT_updates_filtered$elev_h_ft, breaks = seq(round_any(min(EDIT_updates_filtered$elev_l_ft), 250, f = floor),
                                                    round_any(max(EDIT_updates_filtered$elev_h_ft), 250, f = ceiling), 250), xaxt = "n",
      main = "Elevation high", xlab = "Elevation (ft)")
axis(side = 1, at = seq(round_any(min(EDIT_updates_filtered$elev_l_ft), 250, f = floor),                                                     round_any(max(EDIT_updates_filtered$elev_h_ft), 250, f = ceiling), 250), 
     labels = seq(round_any(min(EDIT_updates_filtered$elev_l_ft), 250, f = floor),                                                     round_any(max(EDIT_updates_filtered$elev_h_ft), 250, f = ceiling), 250))}

{hist(EDIT_updates_filtered$elev_l_ft, breaks = seq(round_any(min(EDIT_updates_filtered$elev_l_ft), 250, f = floor),
                                                    round_any(max(EDIT_updates_filtered$elev_h_ft), 250, f = ceiling), 250), xaxt = "n",
      main = "Elevation low", xlab = "Elevation (ft)")
axis(side = 1, at = seq(round_any(min(EDIT_updates_filtered$elev_l_ft), 250, f = floor),                                                     round_any(max(EDIT_updates_filtered$elev_h_ft), 250, f = ceiling), 250), labels = seq(round_any(min(EDIT_updates_filtered$elev_l_ft), 250, f = floor),                                                     round_any(max(EDIT_updates_filtered$elev_h_ft), 250, f = ceiling), 250))}

{hist(EDIT_updates_filtered$elev_r_ft, breaks = seq(round_any(min(EDIT_updates_filtered$elev_l_ft), 250, f = floor),                                                     round_any(max(EDIT_updates_filtered$elev_h_ft), 250, f = ceiling), 250), xaxt = "n",
      main = "Elevation representative", xlab = "Elevation (ft)")
axis(side = 1, at = seq(round_any(min(EDIT_updates_filtered$elev_l_ft), 250, f = floor),                                                     round_any(max(EDIT_updates_filtered$elev_h_ft), 250, f = ceiling), 250), labels = seq(round_any(min(EDIT_updates_filtered$elev_l_ft), 250, f = floor),                                                     round_any(max(EDIT_updates_filtered$elev_h_ft), 250, f = ceiling), 250))}
```

Elevation (high) summary
```{r}
summary(EDIT_updates_filtered$elev_h_ft)
```

Elevation (low) summary
```{r}
summary(EDIT_updates_filtered$elev_l_ft)
```

Elevation (representative) summary
```{r}
summary(EDIT_updates_filtered$elev_r_ft)
```

**Slope**
```{r, fig.show="hold", out.width="50%"}
{hist(EDIT_updates_filtered$slope_h, breaks = seq(0, 200, 10), xaxt = "n",
      main = "Slope high", xlab = "Slope (%)")
axis(side = 1, at = seq(0, 200, 10), 
     labels = seq(0, 200, 10))}

{hist(EDIT_updates_filtered$slope_l, breaks = seq(0, 200, 10), xaxt = "n",
      main = "Slope low", xlab = "Slope (%)")
axis(side = 1, at = seq(0, 200, 10), labels = seq(0, 200, 10))}

{hist(EDIT_updates_filtered$slope_r, breaks = seq(0, 200, 10), xaxt = "n",
      main = "Slope representative", xlab = "Slope (%)")
axis(side = 1, at = seq(0, 200, 10), labels = seq(0, 200, 10))}
```

Slope low
```{r}
summary(EDIT_updates_filtered$slope_l)
```

Slope high
```{r}
summary(EDIT_updates_filtered$slope_h)
```

Slope representative
```{r}
summary(EDIT_updates_filtered$slope_r)
```


**Water table depth**

If ecosite does not seem to be associated with a water table, enter "NA"
```{r, fig.show="hold", out.width="50%"}

if (all(is.na(EDIT_updates_filtered$water_table_l_in))) {print("No recorded values for water table low. Enter NA.")
  
} else{
  {hist(EDIT_updates_filtered$water_table_l_in, breaks = seq(plyr::round_any(min(EDIT_updates_filtered$water_table_l_in, na.rm = TRUE), 10, f = floor),
                                                    plyr::round_any(max(EDIT_updates_filtered$water_table_h_in + 1, na.rm = TRUE), 10, f = ceiling), 10), xaxt = "n",
      main = "Water table depth - low", xlab = "Depth (in)")
axis(side = 1, at = seq(round_any(min(EDIT_updates_filtered$water_table_l_in, na.rm = TRUE), 10, f = floor),
                                                    round_any(max(EDIT_updates_filtered$water_table_h_in + 1, na.rm = TRUE), 10, f = ceiling), 10),
     labels = seq(round_any(min(EDIT_updates_filtered$water_table_l_in, na.rm = TRUE), 10, f = floor),
                                                    round_any(max(EDIT_updates_filtered$water_table_h_in + 1, na.rm = TRUE), 10, f = ceiling), 10))}
  
}


if (all(is.na(EDIT_updates_filtered$water_table_h_in))) {print("No recorded values for water table high. Enter NA.")
  
} else{
  {hist(EDIT_updates_filtered$water_table_h_in, breaks = seq(round_any(min(EDIT_updates_filtered$water_table_l_in, na.rm = TRUE), 10, f = floor),
                                                    round_any(max(EDIT_updates_filtered$water_table_h_in + 1, na.rm = TRUE), 10, f = ceiling), 10), xaxt = "n",
      main = "Water table depth - high", xlab = "Depth (in)")
axis(side = 1, at = seq(round_any(min(EDIT_updates_filtered$water_table_l_in, na.rm = TRUE), 10, f = floor),
                                                    round_any(max(EDIT_updates_filtered$water_table_h_in + 1, na.rm = TRUE), 10, f = ceiling), 10),
     labels = seq(round_any(min(EDIT_updates_filtered$water_table_l_in, na.rm = TRUE), 10, f = floor),
                                                    round_any(max(EDIT_updates_filtered$water_table_h_in + 1, na.rm = TRUE), 10, f = ceiling), 10))}
  
}
```

```{r}
EDIT_updates_filtered_for_pie_h <- ifelse(is.na(EDIT_updates_filtered$water_table_h_in) | EDIT_updates_filtered$water_table_h_in == "", "no water table", "water table present")
pie(table(EDIT_updates_filtered_for_pie_h), main = "Proportion with/without water table high")


EDIT_updates_filtered_for_pie_l <- ifelse(is.na(EDIT_updates_filtered$water_table_l_in) | EDIT_updates_filtered$water_table_l_in == "", "no water table", "water table present")
pie(table(EDIT_updates_filtered_for_pie_l), main = "Proportion with/without water table low")


as.data.frame(table(EDIT_updates_filtered$water_table_h_in, useNA = "always")) %>%
  rename('Water table depth high' = Var1) %>% arrange(desc(Freq))

as.data.frame(table(EDIT_updates_filtered$water_table_l_in, useNA = "always")) %>%
  rename('Water table depth low' = Var1) %>% arrange(desc(Freq))
```



**Aspect**

If aspect is not strongly associated with a particular aspect, select "not applicable"
```{r}
hist(EDIT_updates_filtered$aspect_rep, breaks = seq(0, 360, 30), 
     main = "Aspect histogram binned by 30 degrees", xlab = "Aspect")
```

#### **Climate features tab:**

This tab should have climate stations selected and data should be autopopulated. If the climate stations are not selected, notify Nate. 

#### **Water features tab:**

Canned statement for both 'Water features narrative' and 'Wetland description':
Due to the topographic position, this site does not have water features or wetlands. 

#### **Soil features tab:**

**Parent material**
```{r, warning=FALSE}
pm_table <- as.data.frame(table(EDIT_updates_filtered$parent_material)) %>% 
  rename(PM = Var1) %>% arrange(desc(Freq))

pandoc.table(pm_table, split.cells = c(60, 10))

PM <- paste(EDIT_updates_filtered$parent_material, collapse = " ")

pm_words <- strsplit(PM, "[[:space:]]+")[[1]]

wordcloud::wordcloud(pm_words)
```

**Surface texture**
```{r}
as.data.frame(table(EDIT_updates_filtered$surf_texture)) %>% 
  rename("Surface texture" = Var1) %>% arrange(desc(Freq))
```

**Drainage class**

Drainage class does not have low, high, and representative. Use your best judgement about defining representative and actual values. 
```{r}
drainage_class_levels <- c("very poorly", "poorly", "somewhat poorly", "moderately well", "well", "somewhat excessively",
                           "excessively")


drainage_factor <- factor(EDIT_updates_filtered$drainage_class, levels = drainage_class_levels[drainage_class_levels %in% EDIT_updates_filtered$drainage_class])

barplot(table(drainage_factor), main = "Drainage class", xlab = "Drainage class (low to high)")

as.data.frame(table(EDIT_updates_filtered$drainage_class)) %>% 
  rename("Drainage class" = Var1) %>% arrange(desc(Freq))
```

**Permeability class**

Permeability class does not have low, high, and representative. Use your best judgement about defining representative and actual values. 

```{r, fig.show="hold", out.width="50%", message=FALSE}
my_levels <- c("very slow", "slow", "moderately slow", "moderate", "moderately rapid", "rapid", "very rapid")

perm_0_10 <- mapvalues(EDIT_updates_filtered$ksat_l_0_10_in, from = c("very low", "low", "moderately low", "moderate", "moderately high",
                                                                      "high", "very high"), to = c("very slow", "slow", "moderately slow", 
                                                                                                   "moderate", "moderately rapid", "rapid",
                                                                                                   "very rapid"))


perm_0_10 <- factor(perm_0_10, levels = my_levels[my_levels %in% perm_0_10])


if(all(is.na(perm_0_10))){print("All permeability values NA.")} else {barplot(table(perm_0_10), main = "Permeability class 0-10 inches", xlab = "Permeability class (low to high)")}

as.data.frame(table(EDIT_updates_filtered$ksat_l_0_10_in)) %>% 
  rename("Permeability class" = Var1) %>% arrange(desc(Freq))
```

**Depth to restrictive layer**
```{r, fig.show="hold", out.width="50%"}
{hist(EDIT_updates_filtered$restrict_depth_h_in, breaks = seq(0,200, 10), xaxt = "n",
      main = "Depth - deep value", xlab = "depth")
axis(side = 1, at = seq(0, 200, 10), labels = seq(0,200, 10))}

{hist(EDIT_updates_filtered$restrict_depth_l_in, breaks = seq(0,200, 10), xaxt = "n",
      main = "Depth - shallow value", xlab = "depth")
axis(side = 1, at = seq(0, 200, 10), labels = seq(0,200, 10))}

{hist(EDIT_updates_filtered$restrict_depth_r_in, breaks = seq(0,200, 10), xaxt = "n",
      main = "Representative depth", xlab = "depth")
axis(side = 1, at = seq(0, 200, 10), labels = seq(0,200, 10))}
```

**Soil depth**

Soil depth is the same as depth to restrictive layer. 


```{r}
summary(EDIT_updates_filtered$restrict_depth_h_in)
summary(EDIT_updates_filtered$restrict_depth_l_in)
summary(EDIT_updates_filtered$restrict_depth_r_in)

EDIT_updates_filtered$dept
```


**Surface frag cover**

Surface frag does not have low, high, and representative. Use your best judgement about defining representative and actual values. 
NOTE: Notice that there is a calculation of what % of frags are zero. This can't be seen in the histogram because it is binned. It is possible that the representative values could be a low of zero and a high of zero if a high percentage are zero. I would say over 75% 0's would be sufficient to have representative 0 to 0. 

```{r}
frags2mm3in <- ifelse(is.na(EDIT_updates_filtered$frags_r_2mm_3in_on_surf), 0, 
                EDIT_updates_filtered$frags_r_2mm_3in_on_surf)

frags3plus <- ifelse(is.na(EDIT_updates_filtered$frags_r_gt_3in_on_surf), 0,
                     EDIT_updates_filtered$frags_r_gt_3in_on_surf)

{hist(frags2mm3in, breaks = seq(0, 100, 10), xaxt = "n", main = "Surface frag 2mm to 3in",
     xlab = "Frag %")
axis(side = 1, at = seq(0, 100, 10), labels = seq(0,100, 10))}

summary(frags2mm3in)
# Percent of frags 2mm - 3in values equal to zero
length(frags2mm3in[frags2mm3in == 0])*100/length(frags2mm3in)

{hist(frags3plus, breaks = seq(0, 100, 10), xaxt = "n", main = "Surface frag 3in+",
     xlab = "Frag %")
axis(side = 1, at = seq(0, 100, 10), labels = seq(0,100, 10))}

summary(frags3plus)
# Percent of frags 3in+ equal to zero
length(frags3plus[frags3plus == 0])*100/length(frags3plus)
```

**Available water capacity**
```{r, fig.show="hold", out.width="50%"}
{hist(EDIT_updates_filtered$awc_l_0_40_in, breaks = seq(0,10, 1), xaxt = "n",
      main = "AWC low", xlab = "depth")
axis(side = 1, at = seq(0, 10, 1), labels = seq(0, 10, 1))}

{hist(EDIT_updates_filtered$awc_h_0_40_in, breaks = seq(0, 10, 1), xaxt = "n",
      main = "AWC high", xlab = "depth")
axis(side = 1, at = seq(0, 10, 1), labels = seq(0, 10, 1))}

{hist(EDIT_updates_filtered$awc_r_0_40_in, breaks = seq(0,20, 1), xaxt = "n",
      main = "Representative awc", xlab = "depth")
axis(side = 1, at = seq(0, 10, 1), labels = seq(0,10, 1))}
```

```{r}
summary(EDIT_updates_filtered$awc_l_0_40_in)
summary(EDIT_updates_filtered$awc_h_0_40_in)
summary(EDIT_updates_filtered$awc_r_0_40_in)
```


**Soil reaction**

There is no pH representative value. Use your best judgement. 

0-10
```{r, fig.show="hold", out.width="50%"}
{hist(EDIT_updates_filtered$pH_h_0_10in, breaks = seq(1,13, 0.5), xaxt = "n",
     main = "pH 0-10 high", xlab = "pH")
axis(side = 1, at = seq(1, 13, 0.5), labels = seq(1, 13, 0.5))}

{hist(EDIT_updates_filtered$pH_l_0_10in, breaks = seq(1, 13, 0.5), xaxt = "n",
     main = "pH 0-10 low", xlab = "pH")
axis(side = 1, at = seq(1, 13, 0.5), labels = seq(1, 13, 0.5))}

```

```{r}
summary(EDIT_updates_filtered$pH_h_0_10in)
summary(EDIT_updates_filtered$pH_l_0_10in)
```

10-40
```{r, fig.show="hold", out.width="50%"}
{hist(EDIT_updates_filtered$pH_h_10_40in, breaks = seq(1,13, 0.5), xaxt = "n",
     main = "pH 10-40 high", xlab = "pH")
axis(side = 1, at = seq(1, 13, 0.5), labels = seq(1, 13, 0.5))}

{hist(EDIT_updates_filtered$pH_l_10_40in, breaks = seq(1,13, 0.5), xaxt = "n",
     main = "pH 10-40 low", xlab = "pH")
axis(side = 1, at = seq(1, 13, 0.5), labels = seq(1, 13, 0.5))}
```

```{r}
summary(EDIT_updates_filtered$pH_h_10_40in)
summary(EDIT_updates_filtered$pH_l_10_40in)
```

**Subsurface frag**

Subsurface frags are depth 0-60in.

2mm-3in
```{r, fig.show="hold", out.width="50%"}
{hist(EDIT_updates_filtered$subsurf_frags_r_2mm.3in, breaks = seq(0, 100, 10),
     main = "Subsurface frags 2mm - 3in", xlab = "Frag %", xaxt = "n")
axis(side = 1, at = seq(0, 100, 10), labels = seq(0, 100, 10))}
```

% frags 2mm-3in equal to zero
```{r}
length(EDIT_updates_filtered$subsurf_frags_r_2mm.3in[EDIT_updates_filtered$subsurf_frags_r_2mm.3in == 0]) * 
  100/length(EDIT_updates_filtered$subsurf_frags_r_2mm.3in)
```

```{r}
summary(EDIT_updates_filtered$subsurf_frags_r_2mm.3in)
```

3in+
```{r}
{hist(EDIT_updates_filtered$subsurf_frags_r_gt_3in, breaks = seq(0, 100, 10),
     main = "Subsurface frags 3in+", xlab = "Frag %", xaxt = "n")
axis(side = 1, at = seq(0, 100, 10), labels = seq(0, 100, 10))}
```

% frags 3in+ equal to zero
```{r}
length(EDIT_updates_filtered$subsurf_frags_r_gt_3in[EDIT_updates_filtered$subsurf_frags_r_gt_3in == 0]) * 
  100/length(EDIT_updates_filtered$subsurf_frags_r_gt_3in)
```

```{r}
summary(EDIT_updates_filtered$subsurf_frags_r_gt_3in)
```


